Complex networks gradus ad parnassum

### 2015-06-03 article.tex
layout enhancement
pequeno acrescimo para relato dos experimentos

\author{R. Fabbri}
 \altaffiliation[Also at ]{S\~ao Carlos Physics Institute of Physics, University of S\~ao Paulo.}%Lines break automatically or can be forced with \\
%\author{B. Author}%
% \email{Second.Author@institution.edu.}
%\affiliation{ 
%Authors' institution and/or address%\\This line break forced with \textbackslash\textbackslash
%}%
%
%\author{C. Author}
% \homepage{http://www.Second.institution.edu/~Charlie.Author.}
%\affiliation{%
%Second institution and/or address%\\This line break forced% with \\
%}%

@@

\section{\label{sec:models}Paradigmatic models}
\subsection{Small-world}
Characteristics, Measures, Generative models.
\subsection{Geographic}
Characteristics, Measures, Generative models.
\subsection{Scale-Free}
Characteristics, Measures, Generative models.
\subsection{Erd\"os-R\'enyi}
Characteristics, Measures, Generative models.
\subsection{Other recurrent network characteristics}
\section{\label{sec:inet}You-networks, I-networks}
\subsection{\label{sec:stabdiff}Stability and differentiation in human social networks}
\subsection{\label{sec:harn}Harnessing}
Procedures, ontologies, data, software, art, anthropological physics, 
future forecast, next steps and future work.

\section{\label{sec:conc}Conclusions}

@@

\section{Software, data and media}
\section{Related works}
\subsection{Articles}
\subsection{Books}
\section{Exercises}
Theory, real data analysis, anthropological physics experiments.

>>>>

\author{R. Fabbri}
 \altaffiliation{S\~ao Carlos Physics Institute of Physics, University of S\~ao Paulo.}%Lines break automatically or can be forced with \\
%\author{B. Author}%
% \email{Second.Author@institution.edu.}
%\affiliation{ 
%Authors' institution and/or address%\\This line break forced with \textbackslash\textbackslash
%}%
%
%\author{C. Author}
% \homepage{http://www.Second.institution.edu/~Charlie.Author.}
%\affiliation{%
%Second institution and/or address%\\This line break forced% with \\
%}%

@@

\section{\label{sec:models}Paradigmatic models}
\subsection{Small-world}
Characteristics, Measures, Generative models.
\subsection{Geographic}
Characteristics, Measures, Generative models.
\subsection{Scale-Free}
Characteristics, Measures, Generative models.
\subsection{Erd\"os-R\'enyi}
Characteristics, Measures, Generative models.
\subsection{Other recurrent network characteristics}
\section{\label{sec:inet}You-networks, I-networks}
\subsection{\label{sec:stabdiff}Stability and differentiation in human social networks}
\subsection{\label{sec:harn}Harnessing}
Procedures, ontologies, data, software, art, anthropological physics, 
future forecast, next steps and future work.
\section{\label{sec:self}Report of self-harnessing}
\subsection{\label{sec:exp}Experiments}
% Ciclos de difusão
% interações efêmeras
\subsection{\label{sec:res}Results}
% Grupos se aproximam para desenvolver o tema
% Grupos se aproximam para fazer experimentos
% Grupos se aproximam para implementar e difundir estas práticas na sociedade civil 
% Grupos se aproximam para implementar e difundir estas práticas no governo
% Convenio ONU com SGPR de beneficiária.
% Tecnologias desenvolvidas
% Conhecimento científico desenvolvido
\section{\label{sec:conc}Conclusions}

@@

\section{Software, data and media}
\section{Related works}
Articles. Books.
\section{Exercises}
Theory, real data analysis, anthropological physics experiments.
